Improved Bounds for Online Balanced Repartitioning

### 2020-04-22 paper/disc20clustering.tex
wip
Migration graph path bound

\maciek{A linear path in reconfiguration graph.}

\subsection{Bounds on the size of a cluster reconfiguration graph}
\label{ssec:cascade}

Now we bound the cost of a single repartition of DET2 independent of $\ell$.
First, we bound the length of each path in one of optimal solutions.

>>>>

\begin{figure}[H]
  \centering
    \includegraphics[width=0.3\textwidth]{figs/substitute}
    \caption{A costly cascade example. On the left: the configuration prior to the merge and the merge of two components (denoted solid). On the right: corresponding migration graph for the optimal (unique) reconfiguration.}
  \end{figure}

In this section we present an example of a merge action that results in a $k/3$(?) length path in an optimal migration graph.

\subsection{Bounds on the size of a migration graph}
\label{ssec:cascade}

In \cite{repartition-disc}, authors trivially bounded the reconfiguration cost for each merge action by $k \cdot \ell$.
This roughly corresponds to migrating every node in every cluster.
Now, we bound the cost of a single repartition of \TAlg as a function of $k$.
Note that the bound of $k \cdot \ell$ is still valid, and the resulting bound is the minimum of these two.

We begin, by bounding the length of each path in one of optimal solutions.
